Insurance choice, decision assistance, and insurer steering

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update ashecon slides

- Public decision assistance in the form of "navigators"
- Private brokers and agents (majority are brokers)

>>>>

- Public decision assistance in the form of "navigators", no commissions
- Private assistance that receives commissions:
  - "certified insurance agent", acts as independent broker (97\%)
  - "plan-based enroller", acts as agent for insurer (3/%)
  - all listed as "agent" in our analysis
